Avoiding the Global Sort: \break A Faster Contour Tree Algorithm: Erratum

### 2021-10-22 erratum/updated/erratum.tex
minor updates

We note that that the algorithm and analysis of computing the join tree still hold (Sections 4 and 8 of~\cite{rs-17}) .

>>>>

We note that that the algorithm and analysis of computing the join tree still hold (Sections 4 and 8 of~\cite{rs-17}). 
Unfortunately, there is no explicit theorem that states the running time bound of computing the join tree. The current
proof merges various arguments directly into an argument for the final theorem. Theorem 8.1 bounds the running time 
of the join tree construction, and is still correct. Section 7 (which is not affected by the errors above)
proves that computing the contour tree of a minimum dominant complex is equivalent to computing
the join tree. Hence, the main theorem (Theorem 1.1)
is true if $f$ is a minimum (or maximum) dominant complex.
